Why there are more species in several small patches vs few large patches:

### 2024-02-27 RunSims.Rmd
Updated manuscript with new figure 5

>>>>

## Figure of spatial patterns

```{r PlotsSpatialPattern, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}
require(cowplot)
require(ggplot2)
require(png)

image_paths <- c("Figures/NoSelection_lambda2_dd15_ps3_before_nsp37.png","Figures/NoSelection_lambda2_dd15_ps3_after_nsp32.png","Figures/NoSelection_lambda2_dd15_ps3_after_lt_nsp3.png",
                 "Figures/NoSelection_lambda2_dd15_ps29_ before_nsp36.png","Figures/NoSelection_lambda2_dd15_ps29_ after_nsp29.png","Figures/NoSelection_lambda2_dd15_ps29_ after_lt_nsp25.png")

plots <- lapply(seq_along(image_paths), function(i) {
  ggdraw() +  draw_image(image_paths[i],scale=0.9)
  #ggplot() + annotation_custom(ggplotGrob(readPNG(image_paths[i])), xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
})

aplots <- plot_grid(plotlist = plots, ncol = 2,
  labels = c('A.', 'B.', 'C.', 'D.','E.','F.'),
  label_fontface = "plain",
  byrow = FALSE
  )
aplots
save_plot("Figures/ModelSpatialPatternComparison.png",aplots,base_width=6,base_height=8,dpi=600)

### 2024-02-27 ms_SLOSS.Rmd
Updated manuscript with new figure 5

Comparing the three versions of the model at $\lambda =2$, for higher dispersal the neutral model tends to have higher richness and Shannon diversity at higher patch sizes, followed by the hierarchical model and the neutral-with-habitat-selection model (Figures 3 & 4). At the lowest patch size, only in the neutral-with-habitat-selection have populations that can survive, because in the other model versions the individuals observed are migrants that cannot establish local populations and become extinct (See Figures S5 - S15). Thus an intermediate patch size with a maximum species richness is not observed for this model.

Examples of the final pattern of species and habitat distributions are shown in Figures S9- S32. Species spatial distributions closely match the spatial distribution previous to the habitat destruction for neutral and neutral-with-habitat-selection models. Is also clearly observed that for the hierarchical model, there is a strong dominance of the more competitive species where Shannon Diversity is very low for a higher dispersal rate (Figure 4 & S23).

>>>>

Comparing the three versions of the model at $\lambda =2$, for higher dispersal the neutral model tends to have higher richness and Shannon diversity at higher patch sizes, followed by the hierarchical model and the neutral-with-habitat-selection model (Figures 3 & 4). At the lowest patch size, only in the neutral-with-habitat-selection have populations that can survive, because in the other model versions the individuals observed are migrants that cannot establish local populations and become extinct (See Figures S5 - S15). Thus an intermediate patch size with a maximum species richness is not observed for this model. Is also clearly observed that for the hierarchical model, there is a strong dominance of the more competitive species where Shannon Diversity is very low for a higher dispersal rate (Figure 4 & S23).

Examples of the spatial patterns of species and habitat distributions are illustrated in Figures 5 and S9-S32. Simulations with the neutral model depict the species' spatial distribution before fragmentation (Figure 5 A & B) and after fragmentation (Figure 5 C to F), with habitat destruction represented in purple areas. Immediately after fragmentation, the species' spatial distributions closely resemble those before habitat destruction, but then the patch compositions diverge. The divergence in patch species composition is more pronounced in the hierarchical model, where small patches tend to be dominated by one species (Figures S17 - S24). The effect of the minimum patch size for survival is also observed (Figure 5 E).

![Examples of species spatial pattern before and after fragmentation for the neutral model.  Simulations were performed using a fixed growth rate ($\lambda=2$), migration rate of 0.0001 and dispersal distance 1.5. A. & B. spatial pattern before fragmentation. C. & D. Spatial pattern after fragmentation where 60% of the habitat was destroyed (Purple color), with patch-sizes 3 (C) and 29 (D).  E. & F. Spatial pattern after 600 time steps where the extinction of populations is observed at smaller patch-size (E)](Figures/ModelSpatialPatternComparison.png)
